---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
# Purpose
The underlying purpose of testthatMockr is to facilitate better unit testing.
It does this by allowing you to use Mock objects in place of real ones, which can make
test setup faster and easier.

Secondly it allows you to confirm certain actions have been taken in interacting with
the mock object. You can check the unit you are testing has made a certain function call
on the mock with defined parameters.

It is mainly designed for use with object oriented development, which may not 
suit everyone's needs.

# Example
The real benefit of using mocks (in my opinion at least) is when you want to test some
part of your code and keep it separate in the test environment from the rest of the 
complexity of your package.

Here's an actual example of usage from something I was playing with. I wanted to check 
my Broker object was talking to my Market, without actually having to build a Market 
object with all the associated data behind it.  

First building a mock Market:
```{r eval=FALSE}
market <- Mock("Market")
```

Next I note the function 'getBar' is something I want to track, and I specify that I 
want it to return a specific value (but this is optional).  
```{r eval=FALSE}
ticker <- "AMP.AX"
AMP.AX <- loadStocks(ticker)[[1]]
timestamp <- "2010-01-04"
mockMethod(market, "getBar", return.value = AMP.AX[timestamp])
```

Then we build and exercise the Broker:  
```{r eval=FALSE}		
broker <- Broker()
broker <- addMarket(broker, market)
bar <- getBar(broker, ticker, timestamp)
```

And we can then check that 'getBar' was called with specific parameters:  
```{r eval=FALSE}
expect_that(market, called_once_with("getBar", ticker, timestamp))
```

Check out the vignette for more examples.


# Installation
From your R console type:
> install.packages("testthatMockr")

# Further details
Check out the vignette for more examples and discussion.
> browseVignettes("testthatMockr")

I've based this package functionality on the Python Mock module. It's might be worth
having a look at that to get an idea of the type of functionality too.

Following is a brief discussion of the main components to testthatMockr:
## Mock objects
Mock objects allow you to mimick the behaviour of other objects, and have control over
certain behaviour as well as record some behaviour. They are often used in test driven
development.

## Mock methods
Once you've created a mock you can assign certain methods to be a 'mock' method. This
means you have full control over the output, and can record how the method was used on 
the mock object.

## Mock assertions
The other main component of the package are several new assertions to be used in 
testthat unit testing. These typically are used to assert that some function call was
 made on the mock object.

